---
title: "Final Take Home"
author: "Kushal"
date: "12/13/2021"
output:
  pdf_document: default
  html_document: default
---

#Problem 11.23

#reading the data

```{r}
children <- read.csv("Children.csv", header = TRUE)
infants <- read.csv("Infants.csv", header = TRUE)
adults <- read.csv("adults.csv", header = TRUE)

```

##building the models using regression for each dataset

```{r}
modelchildren <- lm(Volume~Weight, data = children)
modelinfants <- lm(Volume~Weight, data = infants)
modeladults <- lm(Volume~Weight, data = adults)


```

#for children
```{r}
summary(modelchildren)
```
#child weighing 18 kg:

V=>0.01807+0.36071 * 18= 6.51

#for infants
```{r}
summary(modelinfants)
```
#infant weighing 9 kg:

V=>0.5040+ 0.3431 * 9= 3.59

#for adults
```{r}
summary(modeladults)
```
 
#adult weighing 78 kg:

V=11.7495+0.1374 * 78= 22.46

#Problem 12.17

```{r}
ci <- matrix(c(72,230,54,192,16,63,8,15), ncol=4, byrow=TRUE)

rownames(ci) <- c("Carriers", "Noncarriers")

colnames(ci) <- c("0","A","B","AB")

```
#chi square implementation
```{r}

ci<- as.table(ci)

chi <- chisq.test(ci)

chi$expected 

chi

```

# Chi-Square Test of Independence:

Ho: no relationship between blood type and one is a carrier or a non-carrier.

Ha: relationship between blood type and one is a carrier or a non-carrier.

P-value: 0.0002246

Conclusion: Reject Ho in favor of Ha. 


#Now conducting the Post-Hoc Analysis below

```{r}
rowsum <- rowSums (ci, na.rm = FALSE, dims = 1)

barplot(ci/rowsum, ylim = c(0,0.65), ylab = "Percents", beside = TRUE, legend = TRUE)

```

